Pareto-Optimal Multistate Protein Design using Tree Graphical Models

### 2013-01-03 docs/tex/experiments.tex
Simulation 7, seqspace

\subsubsection{Simulation Experiment 7: Vary Seq space }

\subsubsection{Simulation Experiment 8: Seq space 20, Vary seq length}

\subsubsection{Simulation Experiment 9 : Jointly vary seq space and length}

\subsubsection{Simulation Experiment 10 : K-way multistate design}

>>>>

\subsubsection{Simulation Experiment 7: Vary Seq space }
\label{sim:seqspace}
Increase the sequence space using random untied feature space as in ~\ref{sim:randfeatsuntied}. Will supply different seq space values. 2,4,16,20 are the values that are goint to be used.

\subsubsection{Simulation Experiment 8: Seq space 20, Vary seq length}
\label{sim:seqlen}
Set the sequence space to be 20 and vary the sequence length from 2^2,2^16

\subsubsection{Simulation Experiment 9 : Jointly vary seq space and length}
\label{sim:seqspacelen}
Jointly vary the sequence space and sequence length,

\subsubsection{Simulation Experiment 10: Vary Feat space }
\label{sim:featspace}
Keeping the seq space at 20, vary feat space from 5-10-25-50

\subsubsection{Simulation Experiment 11: Vary Feat space and sequence length}
\label{sim:featspacelen}
Keeping the seq space at 20, vary feat space from 5-10-25-50, sequence length from 2^2,2^16

\subsubsection{Simulation Experiment : K-way multistate design}

\subsection{Simulation Experiment 11 : Augmenting Feature space}
